Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-25 Methods-and-Results.tex
AOT-P contact hypothesis added rendered

The study itself consisted of three main parts, an introductory
pre-measurement, and the daily experience sampling measurements, as well
as a concluding post-measurement. After giving informed consent,
participants started by filling in an online pre-questionnaire assessing
demographics and general information about their immigration. Over the
next thirty days, the participants then were invited twice a day (at 12
pm and 7pm) to reflect upon their interactions, psychological need
fulfillments, and current attitudes towards the Dutch outgroup
(\textit{median duration} = 22, \textit{MAD duration} = 19). After the
final day of daily diary measurements, participants were invited to fill
in a longer post measurement survey that mirrored the pre-measurement.
All key variables in for this study were part of the short daily diary
surveys.

@@

@@

>>>>

The study itself consisted of three main parts, an introductory
pre-measurement, and the daily experience sampling measurements, as well
as a concluding post-measurement. After giving informed consent,
participants started by filling in an online pre-questionnaire assessing
demographics and general information about their immigration. Over the
next thirty days, the participants then were invited twice a day (at 12
pm and 7pm) to reflect upon their interactions, psychological need
fulfillments, and current attitudes towards the Dutch outgroup
(\textit{median duration} = 22, \textit{MAD duration} = 19). General
compliance was high (85.90\% of all invited surveys were filled
in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%)}.
The response rates were approximately equal during mornings (\textit{n}
= 621) and afternoons (\textit{n} = 604) and most measurements were
completed within four hours of the invitation. After the final day of
daily diary measurements, participants were invited to fill in a longer
post measurement survey that mirrored the pre-measurement. All key
variables in for this study were part of the short daily diary surveys.

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# correlation panel}
\FunctionTok{pairs.panels.new}\NormalTok{(}
\NormalTok{  dtWorkerSupp}\SpecialCharTok{$}\NormalTok{workerAvFreQual }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{select}\NormalTok{(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),}
  \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}
    \StringTok{"Sum:}\SpecialCharTok{\textbackslash{}n}\StringTok{Numer of beeps with Outgroup Contact (NL)"}\NormalTok{,}
    \StringTok{"Sum:}\SpecialCharTok{\textbackslash{}n}\StringTok{Number of Outgroup Contacts (NL)"}\NormalTok{,}
    \StringTok{"Mean:}\SpecialCharTok{\textbackslash{}n}\StringTok{Interaction Quality"}\NormalTok{,}
    \StringTok{"Mean:}\SpecialCharTok{\textbackslash{}n}\StringTok{Outgroup Attitudes (NL)"}
\NormalTok{  )}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{Figures/WorkerFreqAttCor-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# correlation panel with interaction sums winsorized}
\FunctionTok{pairs.panels.new}\NormalTok{(}
\NormalTok{  dtWorkerSupp}\SpecialCharTok{$}\NormalTok{workerAvFreQual }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{select}\NormalTok{(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),}
  \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}
    \StringTok{"Sum:}\SpecialCharTok{\textbackslash{}n}\StringTok{Numer of beeps with Outgroup Contact (NL)}\SpecialCharTok{\textbackslash{}n}\StringTok{[Winsorized]"}\NormalTok{,}
    \StringTok{"Sum:}\SpecialCharTok{\textbackslash{}n}\StringTok{Number of Outgroup Contacts (NL)}\SpecialCharTok{\textbackslash{}n}\StringTok{[Winsorized]"}\NormalTok{,}
    \StringTok{"Mean:}\SpecialCharTok{\textbackslash{}n}\StringTok{Interaction Quality"}\NormalTok{,}
    \StringTok{"Mean:}\SpecialCharTok{\textbackslash{}n}\StringTok{Outgroup Attitudes (NL)"}
\NormalTok{  )}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{Figures/WorkerFreqAttCor-2.pdf}

@@

We tested the most general contact hypothesis in two steps. First, we
assessed whether more intergroup interactions were related to to more
positive outgroup attitudes. Second, we tested whether a potential
positive effect on outgroup attitudes depended on the interaction
quality (jointly with the number of interactions). We find that neither
the number of interactions nor the number of daily diary responses with
an interaction were significantly related with the average outgroup
attitudes. This is to say that within our data, participants with more
outgroup interactions did not have significantly more positive outgroup
attitudes. This might be due to the aggregation within the participants
or the small sample size of between participant data. Nonetheless, the
aggregate data does not support the notion that simply having more
interactions with an outgroup results in more positive outgroup
attitudes.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# create list to store Worker models}
\NormalTok{mdlWorker }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{()}

\CommentTok{\# regression}
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{lmAttFreqQualX }\OtherTok{\textless{}{-}}
  \FunctionTok{lm}\NormalTok{(AvAttitude }\SpecialCharTok{\textasciitilde{}}\NormalTok{ SumContactNL }\SpecialCharTok{*}\NormalTok{ AvQuality, }\AttributeTok{data =}\NormalTok{ dtWorkerSupp}\SpecialCharTok{$}\NormalTok{workerAvFreQual)}
\CommentTok{\# summary(lmWorkerAttFreqQualX)}

\FunctionTok{summ}\NormalTok{(}
\NormalTok{  mdlWorker}\SpecialCharTok{$}\NormalTok{lmAttFreqQualX,}
  \AttributeTok{confint =} \ConstantTok{TRUE}\NormalTok{,}
  \AttributeTok{digits =} \DecValTok{3}\NormalTok{,}
  \AttributeTok{center =} \ConstantTok{TRUE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[!h]
\centering
\begin{tabular}{lr}
\toprule
\cellcolor{gray!6}{Observations} & \cellcolor{gray!6}{21 (2 missing obs. deleted)}\\
Dependent variable & AvAttitude\\
\cellcolor{gray!6}{Type} & \cellcolor{gray!6}{OLS linear regression}\\
\bottomrule
\end{tabular}
\end{table} \begin{table}[!h]
\centering
\begin{tabular}{lr}
\toprule
\cellcolor{gray!6}{F(3,17)} & \cellcolor{gray!6}{6.663}\\
R² & 0.540\\
\cellcolor{gray!6}{Adj. R²} & \cellcolor{gray!6}{0.459}\\
\bottomrule
\end{tabular}
\end{table} \begin{table}[!h]
\centering
\begin{threeparttable}
\begin{tabular}{lrrrrr}
\toprule
  & Est. & 2.5\% & 97.5\% & t val. & p\\
\midrule
\cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{70.930} & \cellcolor{gray!6}{66.519} & \cellcolor{gray!6}{75.341} & \cellcolor{gray!6}{33.927} & \cellcolor{gray!6}{0.000}\\
SumContactNL & 0.269 & -0.150 & 0.688 & 1.354 & 0.193\\
\cellcolor{gray!6}{AvQuality} & \cellcolor{gray!6}{0.765} & \cellcolor{gray!6}{0.288} & \cellcolor{gray!6}{1.242} & \cellcolor{gray!6}{3.385} & \cellcolor{gray!6}{0.004}\\
SumContactNL:AvQuality & -0.049 & -0.085 & -0.014 & -2.954 & 0.009\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Standard errors: OLS; Continuous predictors are mean-centered.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{lmAttFreqQualXEta }\OtherTok{\textless{}{-}}
\NormalTok{  effectsize}\SpecialCharTok{::}\FunctionTok{eta\_squared}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmAttFreqQualX, }\AttributeTok{partial =} \ConstantTok{TRUE}\NormalTok{)}

\NormalTok{interactions}\SpecialCharTok{::}\FunctionTok{interact\_plot}\NormalTok{(}
\NormalTok{  mdlWorker}\SpecialCharTok{$}\NormalTok{lmAttFreqQualX,}
  \AttributeTok{pred =}\NormalTok{ AvQuality,}
  \AttributeTok{modx =}\NormalTok{ SumContactNL,}
  \AttributeTok{interval =} \ConstantTok{TRUE}\NormalTok{,}
  \AttributeTok{partial.residuals =} \ConstantTok{TRUE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{Figures/workerModelOlsAttFreqQual-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{interactions}\SpecialCharTok{::}\FunctionTok{johnson\_neyman}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmAttFreqQualX,}
                             \AttributeTok{pred =}\NormalTok{ AvQuality,}
                             \AttributeTok{modx =}\NormalTok{ SumContactNL,}
                             \AttributeTok{alpha =}\NormalTok{ .}\DecValTok{05}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## JOHNSON-NEYMAN INTERVAL 
## 
## When SumContactNL is OUTSIDE the interval [23.66, 75.42], the slope of AvQuality is p < .05.
## 
## Note: The range of observed values of SumContactNL is [2.00, 51.00]
\end{verbatim}

\includegraphics{Figures/workerModelOlsAttFreqQual-2.pdf}

However, despite the missing relationship with the number of
interactions, we find a medium sized correlation between the
participants' Average Interaction Quality and their Average Outgroup
Attitudes. Thus within our data participants with a higher quality
outgroup interactions also held more positive attitudes towards that
group. And when considering the number of interactions and average
interaction quality jointly in a linear regression, we additionally find
a statistically significant interaction term (\textit{b} = -0.05,
\textit{t}(17) = -2.95, \textit{p} = 0.009, \(\eta_p^2\) = 0.34).
Looking at a floodlight analysis of the effect, we find that in our
sample with an increasing number of interactions the positive effect of
average interaction quality becomes weaker. However, it should be noted
that this is based on data aggregating all within participant nuances
and is only the date of 21 people.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Create and save Model}
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{lmerAttNull }\OtherTok{\textless{}{-}}
\NormalTok{  lme4}\SpecialCharTok{::}\FunctionTok{lmer}\NormalTok{(thermometerDutch\_1 }\SpecialCharTok{\textasciitilde{}} \DecValTok{1} \SpecialCharTok{+}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{|}\NormalTok{ PID),}
    \AttributeTok{data =}\NormalTok{ dtWorker}\SpecialCharTok{$}\NormalTok{full}
\NormalTok{  ) }\CommentTok{\# use optim if it does not converge}

\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{lmeAttNull }\OtherTok{\textless{}{-}}
  \FunctionTok{lme}\NormalTok{(}
\NormalTok{    thermometerDutch\_1 }\SpecialCharTok{\textasciitilde{}} \DecValTok{1}\NormalTok{,}
    \AttributeTok{random =} \SpecialCharTok{\textasciitilde{}} \DecValTok{1} \SpecialCharTok{|}\NormalTok{ PID,}
    \AttributeTok{data =}\NormalTok{ dtWorker}\SpecialCharTok{$}\NormalTok{full,}
    \AttributeTok{control =} \FunctionTok{list}\NormalTok{(}\AttributeTok{opt =} \StringTok{"nlmimb"}\NormalTok{)}
\NormalTok{  ) }\CommentTok{\# use optim if it does not converge}

\CommentTok{\# Get summary with p{-}values (Satterthwaite\textquotesingle{}s method)}
\CommentTok{\# summary(lmerWorkerAttNull) \#or with the lme function}
\FunctionTok{summ}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmerAttNull, }\AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{center =} \ConstantTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[!h]
\centering
\begin{tabular}{lr}
\toprule
\cellcolor{gray!6}{Observations} & \cellcolor{gray!6}{1225}\\
Dependent variable & thermometerDutch\_1\\
\cellcolor{gray!6}{Type} & \cellcolor{gray!6}{Mixed effects linear regression}\\
\bottomrule
\end{tabular}
\end{table} \begin{table}[!h]
\centering
\begin{tabular}{lr}
\toprule
\cellcolor{gray!6}{AIC} & \cellcolor{gray!6}{8805.880}\\
BIC & 8821.213\\
\cellcolor{gray!6}{Pseudo-R² (fixed effects)} & \cellcolor{gray!6}{0.000}\\
Pseudo-R² (total) & 0.698\\
\bottomrule
\end{tabular}
\end{table} \begin{table}[!h]
\centering
\begin{threeparttable}
\begin{tabular}{lrrrrr}
\toprule
\multicolumn{6}{c}{Fixed Effects} \\
\cmidrule(l{3pt}r{3pt}){1-6}
  & Est. & S.E. & t val. & d.f. & p\\
\midrule
\cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{71.338} & \cellcolor{gray!6}{2.695} & \cellcolor{gray!6}{26.466} & \cellcolor{gray!6}{22.053} & \cellcolor{gray!6}{0.000}\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item  p values calculated using Satterthwaite d.f. ; Continuous predictors are mean-centered.
\end{tablenotes}
\end{threeparttable}
\end{table} \begin{table}[!h]
\centering
\begin{tabular}{lll}
\toprule
\multicolumn{3}{c}{Random Effects} \\
\cmidrule(l{3pt}r{3pt}){1-3}
Group & Parameter & Std. Dev.\\
\midrule
\cellcolor{gray!6}{PID} & \cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{12.797}\\
Residual &  & 8.425\\
\bottomrule
\end{tabular}
\end{table} \begin{table}[!h]
\centering
\begin{tabular}{lrl}
\toprule
\multicolumn{3}{c}{Grouping Variables} \\
\cmidrule(l{3pt}r{3pt}){1-3}
Group & \# groups & ICC\\
\midrule
\cellcolor{gray!6}{PID} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{0.698}\\
\bottomrule
\end{tabular}
\end{table}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# generate 95\% parametric bootstrap CIs (and save them as a csv{-}file):}
\CommentTok{\# write.csv(confint(lmer(thermometerDutch\_1\textasciitilde{}1 + (1|PID),data=dtWorker$full),}
\CommentTok{\#                  method="boot",nsim=1000,}
\CommentTok{\#                  parallel = "multicore", ncpus = 4, seed = 42),}
\CommentTok{\#          "output/tables/ML{-}Null{-}CI.csv")}

\CommentTok{\# Save variances}
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull }\OtherTok{\textless{}{-}} 
  \FunctionTok{VarCorr}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmeAttNull) }\CommentTok{\# save variances}
\CommentTok{\# The estimate of (between{-}group or Intercept variance, tau\_\{00\}\^{}2):}
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{tauAttNull }\OtherTok{\textless{}{-}} 
  \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{])}
\CommentTok{\# and the estimate of (within{-}group or residual variance, sigma\^{}2) is:}
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{sigmaAttNull }\OtherTok{\textless{}{-}} 
  \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{2}\NormalTok{])}
\CommentTok{\# The ICC estimate (between/between+within) is:}
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{IccAttNull }\OtherTok{\textless{}{-}}
\NormalTok{  (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{]) }\SpecialCharTok{/}\NormalTok{ (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{]) }\SpecialCharTok{+} \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{2}\NormalTok{])))}
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{IccPercAttNull }\OtherTok{\textless{}{-}}
\NormalTok{  ((}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{]) }\SpecialCharTok{/}\NormalTok{ (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{]) }\SpecialCharTok{+} \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{2}\NormalTok{])))) }\SpecialCharTok{*} \DecValTok{100}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Create and save Model}
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{lmeInterceptAttType }\OtherTok{\textless{}{-}}
  \FunctionTok{lme}\NormalTok{(}
\NormalTok{    thermometerDutch\_1 }\SpecialCharTok{\textasciitilde{}}\NormalTok{ OutgroupInteraction }\SpecialCharTok{+}\NormalTok{ NonOutgroupInteraction,}
    \AttributeTok{random =}  \SpecialCharTok{\textasciitilde{}} \DecValTok{1} \SpecialCharTok{|}\NormalTok{ PID,}
    \AttributeTok{data =}\NormalTok{ dtWorkerSupp}\SpecialCharTok{$}\NormalTok{workerInteractionType}
\NormalTok{  )}

\CommentTok{\# Get summary with p{-}values (Satterthwaite\textquotesingle{}s method)}
\FunctionTok{summ}\NormalTok{(}
\NormalTok{  mdlWorker}\SpecialCharTok{$}\NormalTok{lmerInterceptAttType }\OtherTok{\textless{}{-}} \FunctionTok{lmer}\NormalTok{(}
\NormalTok{    thermometerDutch\_1 }\SpecialCharTok{\textasciitilde{}}\NormalTok{ OutgroupInteraction }\SpecialCharTok{+}\NormalTok{ NonOutgroupInteraction }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{|}\NormalTok{ PID),}
    \AttributeTok{data =}\NormalTok{ dtWorkerSupp}\SpecialCharTok{$}\NormalTok{workerInteractionType}
\NormalTok{  ),}
  \AttributeTok{confint =} \ConstantTok{TRUE}\NormalTok{,}
  \AttributeTok{digits =} \DecValTok{3}\NormalTok{,}
  \AttributeTok{center =} \ConstantTok{FALSE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[!h]
\centering
\begin{tabular}{lr}
\toprule
\cellcolor{gray!6}{Observations} & \cellcolor{gray!6}{1225}\\
Dependent variable & thermometerDutch\_1\\
\cellcolor{gray!6}{Type} & \cellcolor{gray!6}{Mixed effects linear regression}\\
\bottomrule
\end{tabular}
\end{table} \begin{table}[!h]
\centering
\begin{tabular}{lr}
\toprule
\cellcolor{gray!6}{AIC} & \cellcolor{gray!6}{8788.218}\\
BIC & 8813.771\\
\cellcolor{gray!6}{Pseudo-R² (fixed effects)} & \cellcolor{gray!6}{0.006}\\
Pseudo-R² (total) & 0.703\\
\bottomrule
\end{tabular}
\end{table} \begin{table}[!h]
\centering
\begin{threeparttable}
\begin{tabular}{lrrrrrr}
\toprule
\multicolumn{7}{c}{Fixed Effects} \\
\cmidrule(l{3pt}r{3pt}){1-7}
  & Est. & 2.5\% & 97.5\% & t val. & d.f. & p\\
\midrule
\cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{70.343} & \cellcolor{gray!6}{65.002} & \cellcolor{gray!6}{75.683} & \cellcolor{gray!6}{25.814} & \cellcolor{gray!6}{22.897} & \cellcolor{gray!6}{0.000}\\
OutgroupInteractionYes & 2.477 & 1.364 & 3.589 & 4.365 & 1204.135 & 0.000\\
\cellcolor{gray!6}{NonOutgroupInteractionyes} & \cellcolor{gray!6}{0.427} & \cellcolor{gray!6}{-0.683} & \cellcolor{gray!6}{1.538} & \cellcolor{gray!6}{0.754} & \cellcolor{gray!6}{1204.911} & \cellcolor{gray!6}{0.451}\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item  p values calculated using Satterthwaite d.f. 
\end{tablenotes}
\end{threeparttable}
\end{table} \begin{table}[!h]
\centering
\begin{tabular}{lll}
\toprule
\multicolumn{3}{c}{Random Effects} \\
\cmidrule(l{3pt}r{3pt}){1-3}
Group & Parameter & Std. Dev.\\
\midrule
\cellcolor{gray!6}{PID} & \cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{12.811}\\
Residual &  & 8.362\\
\bottomrule
\end{tabular}
\end{table} \begin{table}[!h]
\centering
\begin{tabular}{lrl}
\toprule
\multicolumn{3}{c}{Grouping Variables} \\
\cmidrule(l{3pt}r{3pt}){1-3}
Group & \# groups & ICC\\
\midrule
\cellcolor{gray!6}{PID} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{0.701}\\
\bottomrule
\end{tabular}
\end{table}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{lmerInterceptAttTypeCI }\OtherTok{\textless{}{-}} \FunctionTok{confint}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmerInterceptAttType)}

\CommentTok{\# Generate 95\% parametric bootstrap CIs (and save them as a csv{-}file):}
\CommentTok{\# write.csv(confint(lmer(thermometerDutch\_1 \textasciitilde{} Contact\_dum + inNonDutch + (1|PID),data=dtWorker$full),}
\CommentTok{\#                  method="boot",nsim=1000, parallel = "multicore",}
\CommentTok{\#                  ncpus = 4, seed = 42),}
\CommentTok{\#          "output/tables/ML{-}Inter{-}CI.csv")}

\CommentTok{\# Compare new model to previous step}
\FunctionTok{anova}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmeAttNull, }
\NormalTok{      mdlWorker}\SpecialCharTok{$}\NormalTok{lmeInterceptAttType) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{as.data.frame}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{call) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}
    \AttributeTok{L.Ratio =} \FunctionTok{round}\NormalTok{(L.Ratio, }\DecValTok{3}\NormalTok{),}
    \StringTok{\textasciigrave{}}\AttributeTok{p{-}value}\StringTok{\textasciigrave{}} \OtherTok{=} \FunctionTok{ifelse}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{p{-}value}\StringTok{\textasciigrave{}}\SpecialCharTok{\textgreater{}=}\NormalTok{.}\DecValTok{001}\NormalTok{, }\FunctionTok{round}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{p{-}value}\StringTok{\textasciigrave{}}\NormalTok{, }\DecValTok{3}\NormalTok{), }\StringTok{"\textless{} .001"}\NormalTok{)}
\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{replace}\NormalTok{(}\FunctionTok{is.na}\NormalTok{(.), }\StringTok{""}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{add\_rownames}\NormalTok{(., }\AttributeTok{var =} \StringTok{"Description"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Description =} \FunctionTok{gsub}\NormalTok{(}\StringTok{".*}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{$"}\NormalTok{, }\StringTok{""}\NormalTok{, Description)) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kbl}\NormalTok{(}
\NormalTok{    .,}
    \AttributeTok{caption =} \StringTok{"Worker: Model Comparison"}\NormalTok{,}
    \AttributeTok{format =} \StringTok{"latex"}\NormalTok{,}
    \AttributeTok{linesep =} \StringTok{""}\NormalTok{,}
    \AttributeTok{booktabs =}\NormalTok{ T,}
    \AttributeTok{align =} \FunctionTok{rep}\NormalTok{(}\StringTok{"c"}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(.)),}
    \AttributeTok{digits =} \DecValTok{3}
\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kable\_styling}\NormalTok{(}\AttributeTok{position =} \StringTok{"left"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:workerModelInterceptAttType}Worker: Model Comparison}
\begin{tabular}[t]{ccccccccc}
\toprule
Description & Model & df & AIC & BIC & logLik & Test & L.Ratio & p-value\\
\midrule
lmeAttNull & 1 & 3 & 8806 & 8821 & -4400 &  &  & \\
lmeInterceptAttType & 2 & 5 & 8788 & 8814 & -4389 & 1 vs 2 & 21.663 & < .001\\
\bottomrule
\end{tabular}
\end{table}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Save variances}
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{varInterceptAttType }\OtherTok{\textless{}{-}} 
\NormalTok{  lme4}\SpecialCharTok{::}\FunctionTok{VarCorr}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmeInterceptAttType)}

\CommentTok{\# The estimate of between{-}group (or Intercept variance) explained:}
\CommentTok{\# Variance Explained = 1 – (Var with Predictor/Var without Predictor)}
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{varBtwInterceptAttType }\OtherTok{\textless{}{-}}
  \DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varInterceptAttType[}\DecValTok{1}\NormalTok{]) }\SpecialCharTok{/} \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{]))}
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{varBtwPercInterceptAttType }\OtherTok{\textless{}{-}}
\NormalTok{  (}\DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varInterceptAttType[}\DecValTok{1}\NormalTok{]) }\SpecialCharTok{/} \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{]))) }\SpecialCharTok{*} \DecValTok{100}
\CommentTok{\# and the estimate of within{-}group (or residual variance) explained is:}
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{varWithinInterceptAttType }\OtherTok{\textless{}{-}}
  \DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varInterceptAttType[}\DecValTok{2}\NormalTok{]) }\SpecialCharTok{/} \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{2}\NormalTok{]))}
\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{varWithinPercInterceptAttType }\OtherTok{\textless{}{-}}
\NormalTok{  (}\DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varInterceptAttType[}\DecValTok{2}\NormalTok{]) }\SpecialCharTok{/} \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{2}\NormalTok{]))) }\SpecialCharTok{*} \DecValTok{100}
\end{Highlighting}
\end{Shaded}

We additionally used a multilevel regression to check whether having an
interaction with an outgroup member had a situational (i.e.,
contemporaneous) effect within the participants. We find that having an
outgroup interaction is indeed associated with significantly more
positive outgroup attitudes within the participants (\textit{b} = 2.48,
\textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
\textit{95\%CI}{[}1.3644, 3.5884{]}), even after controlling for having
an interaction with a non-Dutch (which did not relate to outgroup
attitudes independently; For full results see Online Supplementary
Materials B).
